Meta-analysis

### 2021-02-10 04_MetaAnalysis.Rmd
Update estimate table, removing the intercept

kable(results_mv[, 2:9],
      align = "lcccccccc",
      booktabs = TRUE,
      caption = "Table ##: Estimated mean mungbean yields for each spray schedule treatment used for mitigating yield losses to powdery mildew in mungbean crops grown in eastern Australia. Yield estimates were calculated from the network meta-analysis of data obtained from grey literature reports. Z and P values indicate statistical significance in comparison to the intercept.")
```

>>>>

kable(results_mv[2:6, 2:9],
      align = "lcccccccc",
      booktabs = TRUE,
      caption = "Table ##: Estimated  mungbean yields mean difference to the no spray control for each spray schedule treatment. Estimates were calculated from the network meta-analysis of data obtained from grey literature reports of field trials undertaken in Eastern Australia. Z and P values indicate statistical significance in comparison to the intercept.")
```
